Group 5 Report

### 2022-08-03 Report/Group 5 report v2.Rmd
Kopi

---
title: "Group 5 Report"
author: "ISSSV1337 Group 5"
date: "2022-08-03"
output:
  pdf_document: 
    toc: true
    highlight: pygments
    extra_dependencies: "subfig"
---

@@

<!--# Vi burde vel ha navnene våre, siden rapporten skal lastes opp på Inspera?-->
<!--# Legg til et sted: The Norwegian Control Committee for Fundraising (Innsamlingskontrollen) also has some very basic financial data and information available about selected charitable organisations.-->

@@

The project chosen for our group was Oslo Philanthropic Exchange (OPX), 
a startup working to develop solutions to assist individuals and 
organisations wanting to donate to charities and designing a socially 
responsible investment strategy. Their main goal is to increase cash 
flow from private groups and individuals to charitable purposes. Therefore, the donor's trust 
in the charities’ abilities to carry out their promises is of paramount significance.

To do this, data from charities need to be collected. OPX’s current 
challenge is data acquisition, as data currently must be collected manually. They therefore wanted a way to automate data collection, for example using web scraping.

>>>>

----
title: "Group 5 Report"
author: "ISSSV1337 Group 5"
date: "2022-08-03"
output:
  pdf_document: 
    toc: true
    highlight: pygments
    extra_dependencies: "subfig"
---

@@

<!--# Vi burde vel ha navnene våre, siden rapporten skal lastes opp på Inspera?-->

<!--# Legg til et sted: The Norwegian Control Committee for Fundraising (Innsamlingskontrollen) also has some very basic financial data and information available about selected charitable organisations.-->

@@

The project assigned to our group was Oslo Philanthropic Exchange (OPX), 
a startup working to develop solutions to assist individuals and 
organisations wanting to donate to charities and designing a socially 
responsible investment strategy. Their main goal is to increase cash 
flow from private groups and individuals to charitable purposes. Therefore, the donor's trust 
in the charities’ abilities to carry out their promises is of paramount significance.

To do this, data from charities need to be collected. One of OPX’s current 
challenges is data acquisition, as data currently must be collected manually. They therefore wanted a way to automate data collection, for example using web scraping.
